Goal Document: Translating Typing Rules into JastAdd

### 2023-02-16 GoalDocument.tex
goaldoc: Add Saioc Hüttel paper to related work
goaldoc: Reorganise previous work

\section{Related work}
\begin{itemize}
  \item
    André Pacak, Sebastian Erdweg, and Tamás Szabó. 2020. A systematic approach to deriving incremental type checkers. Proc. ACM Program. Lang. 4, OOPSLA, Article 127 (November 2020), 28 pages. https://doi.org/10.1145/3428195 \\
    \url{https://szabta89.github.io/publications/inca-typechecking.pdf} \\
    A paper about implementing a compiler, capable of deriving incremental type checking from typing rules.
    Similar goal to ours, but with a significantly different compilation target, meaning we will likely differ in architecture and what trade-offs are made.

  \item
    Mikael Pettersson. 1996. A Compiler for Natural Semantics. In Proceedings of the 6th International Conference on Compiler Construction (CC '96). Springer-Verlag, Berlin, Heidelberg, 177–191. \\
    \url{https://link.springer.com/chapter/10.1007/3-540-61053-7\_61} \\

@@

>>>>

\section{Related work}
A paper about implementing a compiler, capable of deriving incremental type checking from typing rules.
Similar goal to ours, but with a significantly different compilation target, meaning we will likely differ in architecture and what trade-offs are made.
\begin{itemize}
  \item
    André Pacak, Sebastian Erdweg, and Tamás Szabó. 2020. A systematic approach to deriving incremental type checkers. Proc. ACM Program. Lang. 4, OOPSLA, Article 127 (November 2020), 28 pages. https://doi.org/10.1145/3428195 \\
    \url{https://szabta89.github.io/publications/inca-typechecking.pdf} \\
\end{itemize}
The following papers are more general compilers for natural semantics, without focusing on type checking.
\begin{itemize}
  \item
    Mikael Pettersson. 1996. A Compiler for Natural Semantics. In Proceedings of the 6th International Conference on Compiler Construction (CC '96). Springer-Verlag, Berlin, Heidelberg, 177–191. \\
    \url{https://link.springer.com/chapter/10.1007/3-540-61053-7\_61} \\

@@

  \item
    Saioc, G., Hüttel, H. (2022). A Tool for Describing and Checking Natural Semantics Definitions of Programming Languages. FROM. \\
    \url{https://arxiv.org/abs/2209.09471}
